---
title: "Testing the login" 
tutorial:
  version: 0.1
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(submittr)
knitr::opts_chunk$set(echo = FALSE) 
# For code checking
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

<!-- the login-mockup.Rmd file does the work of connecting to the 
     password and event database. In login-mockup.Rmd, you could have
     other logging destinations ...
     -  options(tutorial.event_recorder = submit_via_cat)
     -  options(tutorial.event_recorder = create_submit_to_file("~/Downloads/eventlog.txt")) 
-->

```{r child = system.file("shiny/login/login-mockup.Rmd", package = "submittr")}
```
 
 
### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two: 

```{r two-plus-two, exercise=TRUE} 

```

```{r two-plus-two-hint, echo = FALSE}
"Not a very useful hint, but a hint."
```

```{r two-plus-two-check, echo=FALSE}
test_1 <- find_call("whatever + whatever",  
            message = "need to use addition (+)")
test_2 <- find_call("2 + whatever", 
            message = "first argument should be 2")
test_3 <- find_call("whatever + 2", 
            message = "second argument should be 2")
test_4 <- check_value(agrees(x == 4), 
            message = "the result should be 4")
USER_CODE %>% test_1 %>% test_2 %>% test_3 %>% final_ %>% test_4
```

```{r, two-plus-two-code-check}
USER_CODE %>% check_blanks() 
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:
 
```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2  

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz 

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## Video

![](https://youtu.be/zNzZ1PfUDNk){width="560" height="315"}
